---
title: "p8105_hw1_aw3621"
author: "Anni Wang"
date: "2024-09-21"
output: github_document
---


```{r}
data("penguins", package = "palmerpenguins")
#names / values of important variables; the size of the dataset (using nrow and ncol); the mean flipper length
names(penguins)
str(penguins)
nrow(penguins)
ncol(penguins)
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
mean_flipper_length

#a scatterplot of flipper_length_mm vs bill_length_mm
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "scatterplot of flipper_length_mm (y) vs bill_length_mm (x)",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")
ggsave("scatterplot.png")

```

Promblem 2
```{r}
library(tidyverse)
```

# Create the data frame

```{r}
hw1_df=
  tibble(
    samp = rnorm(10), 
    vec_logical= samp > 0, 
    vec_char = letters[1:10],  
    vec_factor= factor(rep(c("1", "2", "3"), length.out = 10))
  )
print(hw1_df)
```

#take the mean of each variable in your dataframe
```{r}
mean_samp= mean(pull(hw1_df,samp), na.rm = TRUE)
mean_samp
mean_vec_logical=mean(pull(hw1_df,vec_logical), na.rm = TRUE)  
mean_vec_logical
mean_vec_char = mean(pull(hw1_df,vec_char), na.rm = TRUE)  
mean_vec_char       
mean_vec_factor= mean(pull(hw1_df,vec_factor), na.rm = TRUE)  
mean_vec_factor
```
The first two of my varibale works, which are logical vector and random sample size of 10. However, there are warning in logical vector and lasr two variables saying that  argument is not numeric or logical: returning NA. 
To fix this, we will use as numeric function:

```{r}
mean_vec_logical=as.numeric(pull(hw1_df,vec_logical), na.rm = TRUE)  
mean_vec_logical
mean_vec_char = as.numeric(pull(hw1_df,vec_char), na.rm = TRUE)  
mean_vec_char       
mean_vec_factor= as.numeric(pull(hw1_df,vec_factor), na.rm = TRUE)  
mean_vec_factor
```
For logical variable, it turns into 1 and 0, 1=true and 0=false. I also got warning says  NAs introduced by coercion.
For character varible, it completely turns into NA.
For factor variable, it turns to numeric variable that I set before from 1 to 3, which can be calculated the mean now.
